From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}

### 2024-01-07 main-elsevier.tex
Final submission

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{url}
\usepackage{tablefootnote}
    \geometry{a4paper}
\bibliographystyle{apalike}

@@

\begin{figure}[t!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
\end{figure}

@@

% Answer: [trim={left bottom right top},clip]
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{Toy/toy-sim.png}
        \caption{Edge similarity matrix from toy example.}
        \label{tab:toy-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{Toy/toy-dis.png}
        \caption{Edge distance matrix from toy example.}
        \label{tab:toy-dis}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy-ex}
 \end{figure}

@@

\begin{figure}[t!]
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/macro.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/macro-lab.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro-labels}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/metal-branches.png}
        \caption{k = 3}
        \label{fig:dend-micro-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Plots/Dend/salsa-branches.png}
        \caption{k = 3}
        \label{fig:dend-micro-salsa}
    \end{subfigure}
    \caption{}
    \label{fig:dend}
 \end{figure}

@@

\begin{figure}[t!]
    \captionsetup[subfigure]{font=footnotesize}
    \caption{Coefficient estimates from Linear Probability Models predicting macrogenre and microgenre choices for Metal and Salsa using socio-demographic predictors.}
    \label{tab:reg}
    \centering    
     \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-metal.png}
        % trim={<left> <lower> <right> <upper>}
        %\includegraphics[width=1.0\textwidth]{}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-salsa.png}
    \end{subfigure}
\end{figure}

@@

\begin{figure}[t!]
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-metal.png}
        \caption{}
        \label{fig:age-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-salsa.png}
        \caption{}
        \label{fig:age-salsa}
    \end{subfigure}
\end{figure}

>>>>

\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
\usepackage{url}
\usepackage{tablefootnote}
    \geometry{a4paper}
\bibliographystyle{apalike}

@@

\begin{figure}[t!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
\end{figure}

@@

% Answer: [trim={left bottom right top},clip]
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{toy-sim.png}
        \caption{Edge similarity matrix from toy example.}
        \label{tab:toy-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{toy-dis.png}
        \caption{Edge distance matrix from toy example.}
        \label{tab:toy-dis}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{link-clust-toy.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy-ex}
 \end{figure}

@@

\begin{figure}[t!]
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{macro.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{macro-lab.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro-labels}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{metal-branches.png}
        \caption{k = 3}
        \label{fig:dend-micro-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{salsa-branches.png}
        \caption{k = 3}
        \label{fig:dend-micro-salsa}
    \end{subfigure}
    \caption{Dendrograms from link clustering procedure on real data.}
    \label{fig:dend}
 \end{figure}

@@

\begin{figure}[t!]
    \captionsetup[subfigure]{font=footnotesize}
    \caption{Coefficient estimates from Linear Probability Models predicting macrogenre and microgenre choices for Metal and Salsa using socio-demographic predictors.}
    \label{tab:reg}
    \centering    
     \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{reg-tab-metal.png}
        % trim={<left> <lower> <right> <upper>}
        %\includegraphics[width=1.0\textwidth]{}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.9\textwidth}
        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{reg-tab-salsa.png}
    \end{subfigure}
\end{figure}

@@

\begin{figure}[t!]
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{micro-by-age-metal.png}
        \caption{}
        \label{fig:age-metal}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \centering    
        \includegraphics[width=1.0\textwidth]{micro-by-age-salsa.png}
        \caption{}
        \label{fig:age-salsa}
    \end{subfigure}
    \caption{Age effects on Metal and Salsa microgenres.}
\end{figure}

### 2024-01-07 title-page.tex
Final submission

\title{From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}}

>>>>

\title{From Macrogenres to Microgenres Via Relationality\footnote{Previous versions of this paper were presented at the University of Notre Dame Sociology Department Culture Workshop, the University of Arizona School of Sociology Brown Bag Series, the Duke University Department of Sociology Jensen Lecture Series, and as a keynote address at the Understanding Everyday Participation Project Closing Conference in Manchester, UK, where I received incisive feedback and questions from various audience members, most of which was incorporated into the first completed draft of the paper. Particular thanks go to Vaughn Schmutz and three \textit{Poetics} anonymous readers whose comments, suggestions, and challenges greatly improved the initial submission.}}
